A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-03-25 paper.tex
Added some high level intuition to the conclusion

SAT-based bounded model checking approaches that unroll the transition relation
have been extended to unbounded by using conflicts in the solver
\cite{mcmillan2002}, or by interpolation \cite{mcmillan2003}. However, there
are no corresponding adaptations to synthesis. Incremental induction
\cite{bradley2011} is another technique for unbounded model checking with an
equivalent synthesis method \cite{morgenstern2013}, which computes the set of
safe states incrementally.

@@

We presented an extension to an existing bounded synthesis technique that
promotes it to unbounded safety games. The approach taken as whole differs from
other synthesis techniques by combining counterexample guided game solving with
winning set computation. The results show that our approach is able to solve
more unique instances than other solvers by performing well on certain classes
of games that are hard for other methodologies.

>>>>

SAT-based bounded model checking approaches that unroll the transition relation
have been extended to unbounded by using conflicts in the solver
\cite{mcmillan2002}, or by interpolation \cite{mcmillan2003}. However, there
are no corresponding adaptations to synthesis.

Incremental induction \cite{bradley2011} is another technique for unbounded
model checking with an equivalent synthesis method \cite{morgenstern2013},
which computes sets of states that overapproximate the losing states (similar
to our $B^m$) and another set of winning states (similar to the negation of
$B^M$). Their algorithm maintains a similar invariant over the sets of losing
states as our approach and has the same termination condition. It differs in
how the sets are computed, which it does by inductively proving the number of
game rounds required by the environment to win from the initial state.

@@

We presented an extension to an existing bounded synthesis technique that
promotes it to unbounded safety games. The approach taken as whole differs from
other synthesis techniques by combining counterexample guided game solving with
winning set computation. Intuitively, the abstraction refinement framework of
the bounded synthesis algorithm restricts the search to consider only moves
that may lead to winning strategies. By constructing sets of bad states during
this search we aim to consider only states that are relevant to a winning
strategy while solving the unbounded game.

The results show that our approach is able to solve more unique instances than
other solvers by performing well on certain classes of games that are hard for
other methodologies.
